### 2018-01-31 Main.Rmd
modif cogsci draft

```{r}
#make a loop
degreeDist <- data.frame(matrix(ncol = 4, nrow = 0))
x <- c("x", "y", "dimension", "language")
colnames(degreeDist) <- x

@@

  #Do the transfomation
  semList <- data_lang$Sem[data_lang$Sem != 0]
  sem_pl = displ$new(semList)
  sem_est = estimate_xmin(sem_pl)
  sem_pl$setXmin(sem_est)
  sem_dist = plot(sem_pl) %>%
    mutate(dimension='Sem', language  =  i)

@@

  dist_lang <- bind_rows(sem_dist, phono_dist)

  degreeDist <- bind_rows(degreeDist, dist_lang)

@@

feather::write_feather(degreeDist, "saved_data/degreeDist.feather")
degreeDist <- feather::read_feather("saved_data/degreeDist.feather")

>>>>

```{r}
#Data for plot
degreeDist <- data.frame(matrix(ncol = 4, nrow = 0))
dist_names <- c("x", "y", "dimension", "language")
colnames(degreeDist) <- dist_names

#Parameters and test
degreeTest <- data.frame(matrix(ncol = 5, nrow = 0))
test_names <- c("xMin", "alpha", "pVal", "dimension","language")
colnames(degreeTest) <- test_names

@@

  #fit and derive parameters for power law
  semList <- data_lang$Sem[data_lang$Sem != 0]
  sem_pl = displ$new(semList)
  sem_est = estimate_xmin(sem_pl)
  sem_pl$setXmin(sem_est)
  sem_dist = plot(sem_pl) %>%
    mutate(dimension='Sem', language  =  i)

  #bootstrap to get p-value
  sem_boot = bootstrap_p(sem_pl, no_of_sims=1000, threads=2)

  sem_test <- data.frame(as.numeric(sem_pl$xmin), as.numeric(sem_pl$pars), as.numeric(sem_boot$p), 'Sem', i)
  colnames(sem_test) <- test_names

@@

  phono_boot = bootstrap_p(phono_pl, no_of_sims=1000, threads=2)

  phono_test <- data.frame(as.numeric(phono_pl$xmin), as.numeric(phono_pl$pars), as.numeric(phono_boot$p), 'Phono', i)
  colnames(phono_test) <- test_names

  dist_lang <- bind_rows(sem_dist, phono_dist)
  test_lang <- bind_rows(sem_test, phono_test)

  degreeDist <- bind_rows(degreeDist, dist_lang) 
  degreeTest <- bind_rows(degreeTest, test_lang)

@@

#feather::write_feather(degreeDist, "saved_data/degreeDist.feather")
degreeDist <- feather::read_feather("saved_data/degreeDist.feather")

feather::write_feather(degreeTest, "saved_data/degreeTest.feather")
degreeTest <- feather::read_feather("saved_data/degreeTest.feather")
